Effects of CHILDREN's programs

### 2020-02-27 paper.Rnw
pdf compiles without errors

\documentclass[12pt, a4paper, titlepage]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage{booktabs}
% \usepackage{bookmark}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
% \usepackage[onehalfspacing]{setspace}
\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
\usepackage[hidelinks]{hyperref}

@@

If you want to cite \textcite{Millstein.2020} inline, use this.
If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
If you want to cite \citeauthor{Millstein.2020} only as authors, use this.

Equation with double index\\

\begin{equation}
\label{ModelProdu}
\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
\end{equation}

List\\

\begin{itemize}
  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
\end{itemize}

% Figure\\
% 
% \begin{figure}
%   \caption{Dispersion in productivity levels}
%   \label{LineDisp}
% 
% <<echo=FALSE>>=
% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
% print(figureLineDisp)
% @
% 
% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent. A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector. After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter. The shaded bars represent recessions as defined by the NBER. The year ticks refer to January 1. The dispersion measures take as their date the middle of the year, July 2. Compare Kehrig (2015), Figure 1.}
% \end{figure}

% Figure \ref{LineDisp}

% <<results='asis', echo=FALSE>>=
% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
% print(tableCyclicDisp, include.rownames = FALSE)
% @

Regression fit output with texreg\\

<<mealsTripsSubsidyRegressions, echo=FALSE, results='asis'>>=
# , message=FALSE, warning=FALSE
# first, read in all Rds objects that you need
# 
mealsNo_sub.lm = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
tripsNo_sub.lm = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
#  
texreg(list(mealsNo_sub.lm, tripsNo_sub.lm), label = "mealsTripsSubsidyRegressions")
@

Table \ref{mealsTripsSubsidyRegressions}
% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
\section{Outline}
Descriptive statistics\\
dynamics of\\ 
(- number of organizations)\\
(- number of beneficiaries)\\
- selected ordinal outcomes, stacked\\
- real total subsidy\\
- real median subsidy per institution\\
- real median subsidy per beneficiary\\
(- which variables have largest variance; also relevant for variable selection)\\

Regressions\\

Questions:\\
effect of\\
- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
- real meals subsidy on number of meals\\
- real trips subsidy on number of trips\\
- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\

Methods:\\
- simple, metric\\
- standardized, metric\\
- cumulative logit\\
- with control variables\\
(- without outliers)\\
(- imputed data)\\

Diff in Diff\\

Outlook for CHILDREN/variable selection\\
- double selection \\
- partition analysis\\
(- correlation matrix)\\
(- factor analysis)\\
- general tips\\

@@

Figure\\

\begin{figure}
  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
  \label{LineDisp}

<<DaytodayskillsSelfworth, echo=FALSE>>=
figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
print(figureDaytodayskillsSelfworth)
@

@@

<<FundamentalDynamicsTest, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
# 
# # first, read in all Rds objects that you need
# 
# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
#  
# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
# 
# fundamental_dynamics <- xtable(fundamental_dynamics,
#                                digits = c(0, 0, 1, 1, 0, 0),
#           caption = "Summary Statistics",
#           align = "lmmmmm", 
#           label = "fundamentalDynamics"
#           )
# print(fundamental_dynamics, include.rownames = FALSE)
@

@@

fundamental_dynamics <- stargazer(fundamental_dynamics,
                                  summary = FALSE,
                               # digits = c(0, 0, 1, 1, 0, 0),
          caption = "Summary Statistics",
          # align = "lmmmmm", 
          label = "fundamentalDynamics"
          )
print(fundamental_dynamics, include.rownames = FALSE)
@
% look up official names of price indices in English

@@

In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet. Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all, most, some, few, and none. For this figure, we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
<<HealthTimePlots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none.}
\end{figure}

In Figure \ref{Health_timeplots}, for the variable 'lessIll_ordered', there is much non available data (lessIll_ordered refers to the share of beneficiaries who are less frequently ill). In all years, most organizations say that most beneficiaries are more healthy. The least stated category is, that all beneficiaries are less ill. That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll_ordered', appears as good as never.

In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet. The least stated category is that some beneficiaries increased their dietary knowledge. The leftover category, few, does not appear.

The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet). Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet. The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet. The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet. The leftover category, few, also does not appear.

\subsection{Selfworth and everyday expertise}

In its yearly surveys, CHILDREN has always asked about the following two variables. These are the shares of beneficiaries with improved self-worth and with broadened everyday expertise. Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all, most, some, few, and none. As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Selfworth and everyday expertise over time}
  \label{Equality_timeplots}
<<EqualityTimePlots, echo=FALSE, message=FALSE>>=
Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(Equality_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables. These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
\end{figure}

Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth). Mostly, the answer is that most beneficiaries in most organizations have more selfworth. The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth. The leftover category, few, does not appear.

In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible. The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.

@@

\begin{itemize}
  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Meals program and the number of meals it dispenses}
  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with improved self-worth}
  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with broadened everyday expertise}
   \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
\end{itemize}

@@

@@

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ms_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds") #control
lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")#outlier meals
lm_ms_o_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex_control.lm.Rds")#outliercontr
lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals

texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE)
@

@@

<<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
lm_ts_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_control.lm.Rds")
lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
lm_ts_o_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex_control.lm.Rds")
lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips

texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE)
@

@@

In their surveys, CHILDREN asks about two variables in both programs. These are the share of beneficiaries with improved self-worth and share of beneficiaries with broadened everyday expertise. This feature could potentially allow us to compare the two programs regarding their realtive effectiveness. Like always, we standardize the two outcome variables. As before, we can only make associational claims. We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes. In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels. 
The four variables are recorded for each year in which the program was operative.
Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.

@@

texreg(list(ss, tss, ssI, tssI ), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
@

@@

texreg(list(ds, tds, dsI, tdsI ), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)

@@

Now, we turn to a predictor that CHILDREN does not directly influence until now, but that it easily could. In 2014, 2016, 2017 and 2018 the organizations had to send CHILDREN a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed those menus with regards to how healthy they were. This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). https://www.schuleplusessen.de/startseite/

In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet. These are the shares of beneficiaries who are less frequently ill, with expanded dietary knowledge and with increased appreciation for a healthy diet.

Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables. For these results, we use their ordinal values. The x-axis displays the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none. For example, if an organization says that most beneficiaries are healthier, then this would be coded as most. In the last reporting period, there are 13 healthy diet criteria. In previous years there were up to 15. The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not. The healthy food incex is calculated as the number of fulfilled criteria. Examples for criteria are daily carbohydrates or daily vegetables.

All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria. The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet. It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy. However, for the variable less ill, the least data is availabe. Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables. This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{Health_Plots}
<<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
print(Health_percentageplots)
@
\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu. It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few, and none}
\end{figure}

We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
By estimating these models with ordinary least squares (OLS), we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so. To control for this difference in size, we additionally fit the models with weighted least squares (WLS), using the number of beneficiaries as weights.

In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant. An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations. Regressing with the imputed dataset, results decrease by about 0.1. Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.

An expanded model with the dependent variable less Ill is presented in Appendix 1 in table \ref{expandLessIll}.

In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant. For the original data set, the coeffiecent is slightly negative. Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations. This coefficent is as well insignifacant.

In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger. For the original data set, the OLS coefficent amounts to 0.27, which is highly significant. When using WLS, we find a slightly negative association. A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02. This coefficent is not significant. For the imputed dataset we find a similar picture.

The regressions with WLS suggest that the results obtained using OLS, are driven by large oraganizations.

@@

Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millenstein.2020, p.677}.

@@

stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill", align = TRUE, label = "lessIllOdds")

>>>>

\documentclass[12pt, a4paper, titlepage]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage{booktabs}
% \usepackage{bookmark}
\usepackage{rotating}
\usepackage{dcolumn}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
% \usepackage[onehalfspacing]{setspace}
\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
\usepackage[hidelinks]{hyperref}

@@

If you want to cite \textcite{Millstein.2020} inline, use this.
If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.
If you want to cite \citeauthor{Millstein.2020} only as authors, use this.

% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}

@@

\begin{figure}
  \caption{Trend in everyday expertise and selfworth}
  \label{DaytodayskillsSelfworth}

<<DaytodayskillsSelfworth, echo=FALSE>>=
figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(figureDaytodayskillsSelfworth)
@

@@

@@

xtable(fundamental_dynamics,
                                  # summary = FALSE,
                                digits = c(0, 0, 1, 1, 0, 0),
           caption = "Summary Statistics",
           align = "lccccc", 
          label = "fundamentalDynamics"
          )

@
% look up official names of price indices in English

@@

In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet. Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For this figure, we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Health outcome over time}
  \label{Health_timeplots}
<<HealthTimePlots, echo=FALSE, message=FALSE>>=
Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
print(Health_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

In Figure \ref{Health_timeplots}, for the variable 'lessIll', there is much non available data. In all years, most organizations say that most beneficiaries are more healthy (3). The least stated category is, that all beneficiaries are less ill(4). That few are less ill (1), appears sometimes and the leftover category,none (0), which is only coded for the variable 'lessIll', appears as good as never.

In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge') mostorganizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet. The least stated category is that some beneficiaries increased their dietary knowledge (2). The leftover category, few (1), does not appear.

The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy'. Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet (3). The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet (4). The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet (2). The leftover category, few, also does not appear.

\subsection{Equality of opportunities releveant variables over time}

In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise. Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.

\begin{figure}
  \caption{Equality of opportunities over time}
  \label{Equality_timeplots}
<<EqualityTimePlots, echo=FALSE, message=FALSE>>=
Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
print(Equality_timeplots)
@
\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities. These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).  
The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
\end{figure}

Figure 4 shows in its upper plot the development of the answered categories for the variable selfworth. Mostly, the answer is that most beneficiaries in most organizations have more selfworth (3). The second most stated category is that all beneficiaries gained in selfworth (4) and the least stated is that some have more selfworth (2). The leftover category, few, does not appear.

In the bottom plot of figure 4 the development of everyday expertise of the beneficiaries over time is visible. The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise (3).

@@

\begin{itemize}
  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Meals program and the number of meals it dispenses}
  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' self-worth}
  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' everyday expertise}
   \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
\end{itemize}

@@

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals

texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
{\\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\\\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\\\ %stars.}", caption.above = TRUE, 
    label = "GrantsRegressionsLunch")
@

@@

@@

<<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips

texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips', digits = 7)
@

@@

In their surveys, CHILDREN asks about two variables in both programs. These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise. This feature could potentially allow us to compare the two programs regarding their realtive effectiveness. Like always, we standardize the two outcome variables. As before, we can only make associational claims. We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes. In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels. 
The four variables are recorded for each year in which the program was operative.
Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.

@@

texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'SelfworthRegressions')
@

@@

texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')

@@

Now, we turn to a predictor that CHILDREN does not directly influence until now, but that it easily could. In 2014, 2016, 2017 and 2018 the organizations had to send CHILDREN a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed those menus with regards to how healthy they were. This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).

In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet. These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.

Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables. The x-axis displays the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none. For example, if an organization says that most beneficiaries are healthier, then this would be coded as most. The highest amount of healthy criteria to be fulfilled is x.

All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria. The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constituted a healthy diet. It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy. However, for the variable less ill, the least data is availabe. Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables. This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{Health_Plots}
<<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
print(Health_percentageplots)
@
\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are. It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them a sample of their menus. An ecotrophologist collaborating with CHILDREN assessed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
By estimating these models with ordinary least squares, we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so. To control for this difference in size, we additionally fit the models with weighted least squares, using the number of beneficiaries as weights.

In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant. An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being more healthy by 0.35 standard deviations. Regressing with the imputed dataset, results decrease by about 0.1. Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.

@@

@@

stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Less Ill", label = "lessIllOdds")
